### 2018-01-26 Graduate - Introduction to Analysis II/HW1/1Homework20180124.tex
add problem 1-3

\documentclass{article}%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{amsfonts}%
\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\def\labelenumi{\arabic{enumi}.}
\def\theenumi{\arabic{enumi}}
\def\labelenumii{(\alph{enumii})}
\def\theenumii{\alph{enumii}}
\def\p@enumii{\theenumi.}
\def\labelenumiii{\arabic{enumiii}.}
\def\theenumiii{\arabic{enumiii}}
\def\p@enumiii{(\theenumi)(\theenumii)}
\def\labelenumiv{\arabic{enumiv}.}
\def\theenumiv{\arabic{enumiv}}
\def\p@enumiv{\p@enumiii.\theenumiii}
\pagestyle{plain}
\setcounter{secnumdepth}{0}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

@@

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 4\\Wednesday, September 27, 2017}\bigskip
\end{center}

\noindent\textbf{Instructions}: This and all subsequent homeworks must be submitted written in \LaTeX.

\noindent If you use results from books, Royden or others, please be explicit about what results you are using.

\begin{center}
\emph{Homework 4 is due by midnight, Saturday, October 7.}
\end{center} 
\medskip

\begin{enumerate}
\item  (Problem 18, Page 63) Let $I$ be a closed bounded interval and let $f$ be a bounded measurable function defined on $I$. Let $\epsilon > 0$.  Show that there is a step function $h$ on $I$ and a measurable subset $F$ of $I$ for which \[
|h-f|< \epsilon \text{ on } F \text{ and } m(I\sim F)< \epsilon .\]

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
For $\epsilon > 0$, according to Lusin's Theorem, there exists a closed subset $F$ of $I$, s.t. $m(I\setminus F) < \epsilon$, and $f$ is continuous on $F$. 
Then for $x_0\in F$, for this $\epsilon > 0$, 
$$
\exists \sigma > 0, ~\forall x\in (x_0-\delta, ~x_0+\delta)\cap F, ~|f(x)-f(x_0)| < \epsilon.
$$
Since
$$
\bigcup_{x_0\in F} (x_0-\delta_i, ~x_0+\delta_i)
$$
is an open cover of the closed set $F$, it has a finite subcover, denoted by
$$
\bigcup_{i=1}^n (x_i-\delta_i, ~x_i+\delta_i).
$$
If we define
$$
h = \left\{
\begin{aligned}
&f(x_i), ~\text{for} ~x\in (x_i-\delta_i, ~x_i+\delta_i), \\
&0, ~\text{others}
\end{aligned}
\right.
$$
then $h$ takes constant values in finite intervals, and $h = 0$ in other parts, we know $h$ is a step function. And from the construction above, on each interval $(x_i-\delta_i, x_i+\delta_i)\cap F$, 
$$
|h-f|< \epsilon ~\text{on}~ (x_i-\delta_i, x_i+\delta_i)\cap F.
$$
Thus $h$ is the step function needed.

\bigskip

\item (Problem 22, Page 64) (Dini's Theorem)  Let $\{f_n\}$ be an increasing sequence of continuous functions on $[a,b]$ which converges pointwise on $[a,b]$ to the continuous function $f$ on $[a,b]$.  Show that the convergence is uniform on $[a,b]$.

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
If the convergence is not uniform, then there $\exists \epsilon > 0, \forall N > 0, ~\exists n > N, ~\exists x\in [a, b], ~|f(x)-f_n(x)| > \epsilon $.

We can construct a sequence $\{x_n\}$ like this:

$$
N = 1, ~\exists n_1 > 1, ~\exists x_1\in[a, b], ~|f_{n_1}(x_1)-f(x_1)| \geqslant \epsilon.
$$
$$
N = n_1, ~\exists n_2 > n_1, ~\exists x_2\in[a, b], ~|f_{n_2}(x_2)-f(x_2)| \geqslant \epsilon.
$$
$$
\cdots
$$
$$
N = n_{k-1}, ~\exists n_k > n_{k-1}, ~\exists x_k\in[a, b], ~|f_{n_k}(x_k)-f(x_k)| \geqslant \epsilon.
$$
$$
\cdots
$$
Then since $x_i\in [a, b]$, according to Bolzano-Weierstrass Theorem, there is a convergent subsequence in $\{x_i\}$, and we may denote it by $\{y_i\}$ for convinence. Assume $y_i\to y\in [a, b]$, then since
$$
\lim_{n\to\infty}f_n(y) = f(y),
$$
for this $\epsilon > 0, ~\exists N$, s.t.
$$
|f_N(y)-f(y)|<\epsilon.
$$
since $f_N$ is continuous, with $y_k\to y$, there $\exists K > 0$, 
$$
|f_N(y_k)-f(y_k)| < \epsilon
$$
holds for all $k > K$. Notice that $\{f_n\}$ is an increasing sequence, when $n > N ~\text{and}~ k > K$, 
$$
|f_n(y_k)-f(y_k)| \leqslant |f_N(y_k)-f(y_k)|<\epsilon.
$$
Since $n_k\to\infty$ when $k\to\infty$, when $k$ is sufficiently large we have $k > K, ~n_k > N$. Thus 
$$
|f_{n_k}(x_k)-f(x_k)| < \epsilon,
$$ 
which makes a contradiction with the assumption. Thus the convergence is uniform.
\bigskip

\item  (Problem 5, Page 364) Show that an extended real-valued function $f$ on $X$ is measurable if and only if for each rational number $c$, $\{x\in X \mid f(x)< c\}$ is a  measurable set.

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
Notice that for each $r\in \mathbb{R}\supset\mathbb{Q}$, we have
$$
\{x\in X\mid f(x) < r\} = \bigcup_{\substack{c < r \\ c \in \mathbb{Q}}}\{x\in X\mid f(x) < c\}.
$$
Then since Lebesgue measurable sets make a $\sigma-$Algebra, we know $\{x\in X\mid f(x) < r\}$ is measurable. On the other hand, since each rational number is a real number, the other direction stands.
\bigskip

\item (Problem 13, Page 365) Let $\{f_n\}$ be a sequence of real-valued functions on $X$ such that for each natural number $n$, $\mu \{x\in X \mid |f_n (x) - f_{n+1}(x)|> 1/2^n\}<1/2^n$. Show that $\{f_n\}$ is pointwise convergent a.e. on $X$.

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
Denote
$$
E_n = \{x\in X\mid |f_n(x)-f_{n+1}(x)|>\frac{1}{2^n}\},
$$
Then 
$$
\bigcup_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\mu(E_n) < \sum_{n=1}^{\infty}\frac{1}{2^n} = 1.
$$
According to Borel-Cantelli Lemma, $\exists E_0$, $\mu(E_0) = 0$, s.t. $\forall x\in X\setminus E_0$, $x$ belongs to at most finite number of $E_n$. That means, $\forall x\in X\setminus E_0$, $\exists N > 0$, $\forall n > N$, $x\in E_n$. So 
$$
|f_n(x)-f_{n+1}(x)| < \frac{1}{2^n}.
$$
Thus 
$$
\forall m > n, |f_m(x)-f_{n}(x)| < \sum_{i=n}^{m-1}|f_{i+1}(x)-f_i(x)| < \frac{1}{2^{n-1}}.
$$
This means that $f_n(x)$ is a Cauchy sequence, then it converges. Thus $\{f_n\}$ is pointwise convergent on $X\setminus E_0$, and thus is pointwise convergent a.e. on $X$.
\bigskip

\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
\begin{enumerate}
\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.
\end{enumerate}

\bigskip
\textbf{Collaborators:} None, but (b) and (c) checked a proof from my Real Analysis textbook in college (Written by Prof. Zhaobo Huang, Fudan University).
\smallskip

\textbf{Solution:}
\textbf{(a)} Since $\{f_n\}$ converges pointwise a.e. on $X$, there $\exists E_0, ~\mu(E_0) = 0$, s.t. $\lim\limits_{n\to\infty}f_n = f$ on $E_1 = X\setminus E_0$. Then $\forall \epsilon > 0$,
$$
E_1 = \bigcup_{k=1}^{\infty} \bigcap_{n=k}^{\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\} = \varliminf_{n\to\infty} \{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}.
$$
Thus, according to the continuity of measure, 
$$
\mu(E_1) \le \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}).
$$
Since $\mu(X) < \infty$, we have
$$
\begin{aligned}
\lim_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| &> \epsilon\}) \le \varlimsup_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| > \epsilon\}) \\
&= \mu(X) - \varliminf_{n\to\infty} \mu(\{x\in E_1\mid |f_n(x)-f(x)| \le \epsilon\}) \le 0.
\end{aligned}
$$
Thus $\{f_n\}$ converges to $f$ in measure.

\textbf{(b)}
Since $\{f_n\}$ converges to $f$ in measure, $\forall k \in \mathbb{N}$, $\exists n_k > n_{k-1} \in \mathbb{N}$, s.t. when $n \ge n_k$,
$$
\mu(\{x\in X\mid |f_n(x)-f(x)| \ge \frac{1}{2^k}\}) < \frac{1}{2^k}.
$$
Denote $E_{k} = \{x\in X\mid |f_{n_k}(x)-f(x)| \ge \frac{1}{2^k}\}$, then $\mu(E_k) < \frac{1}{2^k}$. Let 
$$
F_k = \bigcap_{i=k}^{\infty} (X\setminus 
E_i) = \{x\in X\mid |f_{n_i}(x)-f(x)|\le \frac{1}{2^i}, i = k, k+1, \cdots\}
$$
then $\{f_{n_k}\}$ converges uniformly to $f$ on $F_k$, thus is convergent on $F = \bigcup\limits_{k=1}^{\infty}F_k$. On the other hand,
$$
X\setminus F = \bigcap_{k=1}^{\infty}(X\setminus F_k) = \bigcap_{k=1}^{\infty}\bigcup_{k=1}^{\infty}E_i = \varlimsup_{i\to\infty}E_i,
$$
and 
$$
\sum_{i=1}^{\infty}\mu(E_i) \le \sum_{i=1}^{\infty}\frac{1}{2^i} = 1, 
$$
thus $\mu(X\setminus F) = 0$, $\{f_{n_k}\}$ converges pointwise a.e. on $X$.

\textbf{(c)} If $\{f_n\}$ is Cauchy in measure, then for each $n_i \in \mathbb{N}$, there $\exists n_{i+1} > n_{i}$, s.t. 
$$
\mu(\{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\})\le \frac{1}{2^i}.
$$
We can denote the subsequence $\{f_{n_i}\}$ as $\{g_i\}$, and $E_i = \{x\in X\mid |f_{n_i}(x)-f_{n_{i+1}}(x)| \ge \frac{1}{2^i}\}$. Let $F_{k} = \bigcup\limits_{i = k}^{\infty}E_i $, then $\mu(F_k)\le \sum\limits_{i=k}^{\infty}\frac{1}{2^i}\le \frac{1}{2^{k-1}} $. Denote $F = \bigcap\limits_{i=1}^\infty F_i $, then $\mu(F) = 0$.

If we choose $x\notin F_{k}$, and $i \ge j \ge k$, then 
$$
|g_i(x)-g_j(x)| \le \sum_{l = j}^{i-1}|g_{l+1}(x)-g_l(x)| \le \frac{1}{2^j},
$$
which means $g_i(x)$ is Cauchy respective to $i$ on $X\setminus F$, thus converges on $X\setminus F$. Thus we can construct a function $f$ like this: 
$$
f(x) = \left\{
\begin{aligned}
&0, ~x\in F \\
&\lim_{i\to\infty}f_i(x), ~x\in X\setminus F.
\end{aligned}
\right.
$$
Then $\{g_i(x)\}$ converges to $f$ on $X\setminus F$, which means $\{g_i\}$ converges pointwise a.e. on $X$. Now we show $\{f_n\}$ converges to $f$ in measure. Notice
$$
\mu(\{x\in X\mid |f_n - f|\ge \xi\}) \le \mu(\{x\mid |f_n-g_m|\ge \frac{\xi}{2}\}) + \mu(\{x\mid |g_m-f|\ge \frac{\xi}{2}\}), ~m > n
$$
and when $n\to\infty$, the two terms in the right can be arbitrarily small, so 
$$
\lim_{n\to\infty}\mu(\{x\in X\mid |f_n - f|\ge \xi\}) = 0, ~\forall \xi > 0.
$$
The $\{f_{n}\}$ converges in measure.
\bigskip

\item (Problem 16, Page 365) Assume $\mu (X) < \infty$.  Show that $\{f_n\}$ converges to $f$ in measure if and only if each  subsequence of $\{f_n\}$ has a further subsequence that converges pointwise a.e. on $X$ to $f$.  Use this to show that for two sequences that converge in measure, the product sequence also converges in measure to the product of the limits.

\bigskip
\textbf{Collaborators:} None
\smallskip

\textbf{Solution:}
\textbf{(1)} Necessity: From $\{f_n\}$ converges to $f$ in measure and the property of convergence, we know that each subsequence of $\{f_n\}$ converges to $f$ in measure. From Problem 5(b) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_{j}}}\}$ converges pointwise a.e. on $X$ to $f$.

Sufficiency: If each subsequence $\{f_{n_k}\}$ has a further subsequence $\{f_{n_{k_j}}\}$ converges pointwise a.e. on $X$ to $f$, then since $\mu(X) < \infty$, from Problem 5(a) we know $\{f_{n_k}\}$ converges in measure to $f$. If $\{f_n\}$ does not converge to $f$ in measure, then there $\exists \epsilon > 0$,
$$
\begin{aligned}
&\text{for}~ n_1 = 1, ~\exists n_2 > n_1, ~\mu(\{x\mid |f_{n_2}-f| \ge \epsilon\}) \ge \epsilon, \\
&\text{for}~ n_2, ~\exists n_3 > n_2, ~\mu(\{x\mid |f_{n_3}-f| \ge \epsilon\}) \ge \epsilon, \\
&\cdots, \\
&\text{for}~ n_k, ~\exists n_{k+1} > n_k, ~\mu(\{x\mid |f_{n_{k+1}}-f| \ge \epsilon\}) \ge \epsilon, \\
&\cdots.
\end{aligned}
$$
Then we get a subsequence $\{f_{n_k}\}$ which does not converge to $f$ in measure. It makes a contratiction.

\textbf{(2)} Suppose $\{f_n\}$, $\{g_n\}$ are two sequences that converge in measure to respectively $f$ and $g$. For each subsequence $\{f_{n_k}g_{n_k}\}$ of $\{f_ng_n\}$, from (1) we know $\{f_{n_k}\}$ has a subsequence $\{f_{n_{k_l}}\}$ converges pointwise a.e. to $f$, and $\{g_{n_{k_l}}\}$ has a subsequence $\{g_{n_{k_{l_j}}}\}$ converges pointwise a.e. to $g$. Since the union of two measure-zero sets is a measure-zero set, we know $\{f_{n_{k_{l_j}}}g_{n_{k_{l_j}}}\}$ converges pointwise a.e. to $fg$ according to the linear property of limits. Thus according to (1) we know $\{f_ng_n\}$ converges in measure to the product of limits.
\bigskip

\item Show that if $f$ is an lower semicontinuous (resp. upper semicontinuous) function on an interval $[a,b]$, then there is a family $\{f_{\alpha}\}$ of continuous functions on the interval $[a,b]$ such that $f(x) = \sup\{f_{\alpha}(x) \mid \alpha \in A \}$ (resp. $f(x) = \inf\{f_{\alpha}(x) \mid \alpha \in A \}$) for all $x \in [a,b]$.

\bigskip
\textbf{Collaborators:} Checked https://people.math.gatech.edu/\~{}loss/16FALLTEA/NOTES/semicontinuity.pdf for help.
\smallskip

\textbf{Solution:}
We first show a lemma.
\begin{lemma}
If $\{f_\alpha(x)\}$ is a family of upper semi-continuous functions, then $\inf\limits_{\alpha\in I}f_\alpha(x)$ is also upper semi-continuous. Conversely, lower semi-continuous is preserved under monotone increasing limits.
\end{lemma}
\begin{proof}
In fact, suppose $\{f_\alpha(x)\}_{\alpha\in I}$ is a family of upper semi-continuous functions, then 
$$
\{x\in [a, b]\mid f_\alpha(x)\ge t\} = \bigcap_{\alpha\in I}\{x\in [a, b]\mid f_\alpha(x)\ge t\}.
$$
With the continuity of $f_\alpha(x)$ and the compactness of $[a, b]$, we know $\{x\in [a, b]\mid f_\alpha(x) \ge t\}$ is closed, so $\{x\in [a, b]\mid f_\alpha(x)\ge t\}$ is also closed. Thus $\inf\limits_{\alpha\in I} f_\alpha(x)$ is upper semi-continuous.
\end{proof}

We just show the case when $f$ is a lower semicontinuous function. Let
$$ 
f_\epsilon(x) = \inf_{y\in [a, b]}\left(f(y) + \frac{|x-y|}{\epsilon}\right),
$$
and we show that $f_\epsilon(x) $ is continuous and converges pointwise to $f$ from below when $\epsilon \to 0^+$.

First, we have $f_\epsilon(x) \le f(x)$ by setting $y = x$ instead of taking the infimum. For each fixed $y\in [a, b]$, the map
$$
x \mapsto f(y)+\frac{|x-y|}{\epsilon}
$$
is continuous, hence according to the lemma, $f_{\epsilon}(x)$ is an upper semi-continuous function.

Since $[a, b]$ is conpact, $f$ is lower semicontinuous, and the map $y\mapsto |x-y|$ is continuous, the infimum is attained, and there exists $y(\epsilon, x) \in [a, b]$, s.t.
$$
f_\epsilon(x) = f(y(\epsilon, x)) + \frac{d(x, y(\epsilon, x))}{\epsilon}.
$$
Pick $\{x_n\}\to x$, then since $[a, b]$ is compact we may assume $y(\epsilon, x) \to y_{0}$. Then since $f_{\epsilon}(x)$ is upper semicontinuous, 
$$
f_\epsilon(x)\ge \varlimsup_{n\to\infty}f_\epsilon(x_n) = \varlimsup_{n\to\infty}f(y(\epsilon, x_n)) + \frac{|x-y_0|}{\epsilon} \ge f(y_0) +\frac{|x-y_0|}{\epsilon} \ge f_\epsilon(x)
$$
Thus $f_\epsilon(x) $ is continuous. When $\epsilon\to 0$, we know $y(\epsilon, x) \to x$, otherwise $\frac{d(x, y(\epsilon, x))}{\epsilon}\to\infty$. And we have
$$
f(x) \ge \varlimsup_{\epsilon \to 0}f_\epsilon(x) = \varlimsup_{\epsilon\to 0}\left(f(y(\epsilon, x))+\frac{d(x, y(\epsilon, x))}{\epsilon}\right) \ge f(x) + \varlimsup_{\epsilon\to 0}\frac{d(x, y(\epsilon, x))}{\epsilon}.
$$
Which means $$\frac{d(x, y(\epsilon, x))}{\epsilon}\to 0,$$
and $f_\epsilon(x) \to f(x)$.
\bigskip

\end{enumerate}
\end{document}

>>>>

\documentclass{article}%

\usepackage{amsmath}

\usepackage{graphicx}

\usepackage{amsfonts}%

\usepackage{amssymb}

\setlength{\topmargin}{-0.75in}

\setlength{\textheight}{9.25in}

\setlength{\oddsidemargin}{0.0in}

\setlength{\evensidemargin}{0.0in}

\setlength{\textwidth}{6.5in}

\def\labelenumi{\arabic{enumi}.}

\def\theenumi{\arabic{enumi}}

\def\labelenumii{(\alph{enumii})}

\def\theenumii{\alph{enumii}}

\def\p@enumii{\theenumi.}

\def\labelenumiii{\arabic{enumiii}.}

\def\theenumiii{\arabic{enumiii}}

\def\p@enumiii{(\theenumi)(\theenumii)}

\def\labelenumiv{\arabic{enumiv}.}

\def\theenumiv{\arabic{enumiv}}

\def\p@enumiv{\p@enumiii.\theenumiii}

\pagestyle{plain}

\setcounter{secnumdepth}{0}

\newtheorem{theorem}{Theorem}

\newtheorem{acknowledgement}[theorem]{Acknowledgement}

\newtheorem{algorithm}[theorem]{Algorithm}

\newtheorem{axiom}[theorem]{Axiom}

\newtheorem{case}[theorem]{Case}

\newtheorem{claim}[theorem]{Claim}

\newtheorem{conclusion}[theorem]{Conclusion}

\newtheorem{condition}[theorem]{Condition}

\newtheorem{conjecture}[theorem]{Conjecture}

\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{criterion}[theorem]{Criterion}

\newtheorem{definition}[theorem]{Definition}

\newtheorem{example}[theorem]{Example}

\newtheorem{exercise}[theorem]{Exercise}

\newtheorem{lemma}[theorem]{Lemma}

\newtheorem{notation}[theorem]{Notation}

\newtheorem{problem}[theorem]{Problem}

\newtheorem{proposition}[theorem]{Proposition}

\newtheorem{remark}[theorem]{Remark}

\newtheorem{solution}[theorem]{Solution}

\newtheorem{summary}[theorem]{Summary}

\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

@@

\begin{center}

\textbf{Homework 1}\bigskip

\end{center}

\noindent\textbf{Instructions}:

\noindent In problems 3. - 5., references such as III.2.7 refer to Problem 7 in Section 2 of Chapter III in Conway's book.\smallskip

\noindent If you use results from books including Conway's, please be explicit about what results you are using.

\begin{center}

\emph{Homework 1 is due on Dropbox on Monday, February  5.}

\end{center}

\medskip

\begin{enumerate}

\item Show that $\lim_{n\to \infty}{n^{\frac{1}{n}}} = 1$ without using logarithms.

\textbf{Proof.} Let $n^{1/n} = 1+y_n $. First we know $n^{1/n} > 1^{1/n} = 1 $, so $y_{n} > 0$. Then 
$$
n = (1+y_n)^n = 1+ny_n+\frac{n(n-1)}{2}y_n^2+\cdots+y_n^n > 1+\frac{n(n-1)}{2}y_n^2.
$$
Thus $\frac{n(n-1)}{2}y_n^2 < n-1 $, which means $y_n < \sqrt{2/n}. $ Hence $\lim\limits_{n\to\infty} y_n \le \lim\limits_{n\to\infty}\sqrt{2/n} = 0$, which means $y_n\to 0 $, and thus $n^{1/n}\to 1 $.

\item Given a power series, $\sum_{n=0}^{n=\infty} a_n(z - a)^n$, show that its radius of convergence $R$ satisfies the inequalities$$(\limsup{\vert \frac{a_{n+1}}{a_n} \vert})^{-1} \leq R \leq \limsup{\vert \frac{a_{n}}{a_{n+1}} \vert}.$$

\textbf{Proof.} We only proof the right inequality since it is just the same for the left one. If $R > r > \limsup|\frac{a_n}{a_{n+1}}| = \alpha $, then there is an $N > 0$ s.t. $r > |a_n/a_{n+1}| $ for all $n \ge N$. Let $B = |a_N|r^N $, then $|a_{N+1}|r^{N+1} = |a_{N+1}|rr^{N} > B $. Hence for all $n > N$ we have $|a_n|r^n > B $, which gives $|a_nz^n| \ge B |z|^n/|r|^n $ when $n > N$. But $|z|/|r| > 1$, which makes $|z|^n/|r|^n \to\infty $ when $n\to\infty$. Hence $\sum a_nz^n $ diverges, so $R \le \alpha$.

\item Problem III.1.6.

\textbf{(a).} By Theorem 1.3, 
$$
\limsup |a_n|^{1/n} = \limsup |a^n|^{1/n} = |a|,
$$
thus $R = \frac{1}{|a|}$.

\textbf{(b).} By Theorem 1.3,
$$
\limsup |a_n|^{1/n} = \limsup |a^{n^2}|^{1/n} = \limsup |a^n| = \left\{
\begin{aligned} 
&0, |a| < 1, \\
&1, |a| = 1, \\
&\infty, |a| > 1.
\end{aligned}
\right.
$$
Thus 
$$
R = \left\{
\begin{aligned}
&\infty, |a| < 1,\\
&1, |a| = 1,\\
&0, |a| > 1.
\end{aligned}
\right.
$$

\textbf{(c).} By Theorem 1.3,
$$
\limsup |a_n|^{1/n} = \limsup |k^n|^{1/n} = k,
$$
thus $R = \frac{1}{k}$.

\textbf{(d).} Since 
$$
\sum_{n=0}^{\infty}|z|^{n!} < \sum_{n=0}^{\infty}|z|,
$$
and the convergence radius of the latter series is $R' = 1$, we know $R\ge 1$. On the other hand, if $R > 1$, pick $1 < |z| = r < R$, then $|z|^{n!} = r^{n!}\to\infty $ when $n\to\infty$, hence the series diverges. Thus $R = 1$.

\item Problem III.1.7

\item Problem III.2.6

\item Problem III.2.7

\item Problem III.2.9.

\item Problem III.2.13

\item Problem III.2.20

\end{enumerate}

\end{document}
